Template for preparing your research report submission to PNAS using Overleaf

### 2020-07-23 Writeup/manuscript.tex
some sort of contribution

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1]{Peter J. Kohler}
\author[b]{Oda \r{A}sgard} 
\author[b]{Alasdair D. F. Clarke}

\affil[a]{Stanford University, Department of Psychology}
\affil[b]{University of Essex, Department of Psychology, Colchester, UK, CO4 3SQ}

@@

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.}

@@

\begin{abstract}
A century of vision research has demonstrated that symmetry contributes to numerous domains of visual perception \cite{RN1311, RN1166,RN1682,RN1824}. In a 2-D image, the four fundamental symmetries, reflection, rotation, translation and glide reflection, can be combined in 17 distinct ways. These 17 “wallpaper” groups \cite{RN1562,RN1563,RN1425} obey a hierarchy, determined by mathematical group theory, where simpler groups are subgroups of more complex ones\cite{RN1711}. Here we measure symmetry-specific Steady-State Visual Evoked Potentials (SSVEPs), and find that the partial ordering of SSVEPs from visual cortex in human participants ($n=25$), preserve the hierarchical relationships between the wallpaper groups in $88.3\%$ (53 out of 60) of cases. This remarkable consistency between the structure of symmetry representations and mathematical group theory, is likely generated over visual development, through implicit learning of regularities in the environment. 
\end{abstract}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../ac_models_eeg_data/plots/subgroup_comprms_Occ_Odd.png}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

>>>>

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a, b, 1]{Peter J. Kohler}
\author[c]{Alasdair D. F. Clarke}

\affil[a]{York University, Department of Psychology, Toronto, ON M3J 1P3, Canada}
\affil[b]{Centre for Vision Research, York University, Toronto, ON, M3J 1P3, Canada}
\affil[c]{Stanford University, Department of Psychology, Stanford, CA 94305, United States}
\affil[d]{University of Essex, Department of Psychology, Colchester, UK, CO4 3SQ}

@@

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Wallpaper groups were discovered in the mid-19th century, and the 17 groups constitute the complete set of possible ways of regularly tiling the 2D-plane. In recent years wallpaper groups have found use in the vision science community, as an ideal stimulus set for studying the perception of symmetries in textures. Here we present brain imaging and psychophysical data on the complete set of wallpaper groups and show the hierarchical organization among wallpaper groups in reflected in both visual cortex activity and performance on a symmetry detection task.}

@@

\begin{abstract}
A century of vision research has demonstrated that symmetry contributes to numerous domains of visual perception \cite{RN1311, RN1166,RN1682,RN1824}. In a 2-D image, the four fundamental symmetries, reflection, rotation, translation and glide reflection, can be combined in 17 distinct ways. These 17 “wallpaper” groups \cite{RN1562,RN1563,RN1425} obey a hierarchy, determined by mathematical group theory, where simpler groups are subgroups of more complex ones\cite{RN1711}. Here we probe representations of symmetries in wallpaper groups using two methods: Steady-State Visual Evoked Potentials (SSVEPs) recorded using EEG and psychophysical detection thresholds. We find that the hierarchical relationships between the wallpaper groups are almost perfectly preserved in both behavior and response amplitudes in visual cortex. This remarkable consistency between the structure of symmetry representations and mathematical group theory, is likely generated over visual development, through implicit learning of regularities in the environment. 
\end{abstract}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../figures/figure1.png}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comprms_Occ_Odd.png}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}
